GVN-Hoist: Hoisting Computations from Branches

### 2016-08-24 hoist.tex
vbe listed

Dhamdhere \cite{dhamdhere1988fast}, Muchnick \cite{steven1997advanced} mention
code hoisting in a data flow framework.

GCC implementation: Hoists top down in a predecessor where the value is in
ANTIC\_IN. This approach may have the problem of hoisting the expression too far
and to mititage that it only hoists expressions when at least one successor
computes it. Hence the algorithm will hoist a limited set of computations.  One
advantage of GCC implementation is that it works in sync with the GVN-PRE such
that when new hoisting opportunities are created by GVN-PRE, code-hoisting will
hoist them.

>>>>

Dhamdhere \cite{dhamdhere1988fast}, Muchnick \cite{steven1997advanced} mention
code hoisting in a data flow framework. A list of Very Busy Expressions are
computed which are hoisted in a basic block where the expression is anticipable
(all the operands are available). This algorithm would hoist as far as possible
without regarding the impact on register pressure and as such a cost model will
be required.

GCC recently got code-hoisting which is implemented as part of GVN-PRE. The
algorithm hoists top down in a predecessor where the value is in ANTIC\_IN. This
approach may have the problem of hoisting the expression too far and to mititage
that it only hoists expressions when at least one successor computes it. Hence
the algorithm will hoist a limited set of computations.  One advantage of GCC
implementation is that it works in sync with the GVN-PRE such that when new
hoisting opportunities are created by GVN-PRE, code-hoisting will hoist them.
